\TheTitle

### 2016-07-25 linvis.tex
In 2004 we are correct, not wrong
Looked more deeply into the issue and found that it is not an error,
it is a HUGE branch created by linus. he committed to a branch on this
with this root 3f17ea6dea8ba5668873afa54628a91aaa3fb1c0.

Fixed grammar issues too.

We used this information to evaluate the accuracy of the merge-tree model extracted from the DAG. The method we followed
started with the extraction of the commit history up to July 20, 2016. We computed the merge tree of every commit until
then. Since Linus Torvalds mostly does merging directly into master, we assumed that every merge by him is the root of a
merge-tree. As described above, the log of a commit usually contains the number of commits in the merge the first 20
summaries of commits being merged. We extracted merges by Linus Torvalds using the command \mycode{log --merges --author='Torvalds} and compared
the number of commits in according to the log with the number of commits in the  merge-tree rooted in this commit. We
also used the summaries of the commits found in the merge (not necessarily all---see above) to make sure those 
commits were in their corresponding merge tree. For example, for the merge in Figure~\ref{sampleMerge} we would expect
that the merge tree rooted at \mycode{8cbd84f} contains 24 commits, and the one-line summaries corresponds to commits in
that merge-tree. We also inspected those with differences to make sure they were true errors.

The results can be summarized as follows:

\begin{itemize}
\item 5 merges were false-erros because their logs did not contain accurate information (were probably edited by
  hand). For example in \mycode{42a579a0f...}) one commit summary was missing (the line was empty), in another  \mycode
  {c55d267}) the summaries were reordered.
\item The heuristic works correctly for all merges except between Jun 7, 2014 and Jun 2, 2014 (92 merges) and before
  Sept 4, 2007. Before this date merges did not include a summary of the commits they included, hence making it
  impossible to verify; however, we correctly identified the merges by Linus into master. 
\item Before Dec. 12, 2006 (1542 merges) our heuristic breaks due to the
presence of \textit{foxtrot} commits, which confound the true master branch of a
repository
\footnote{See \url{http://bit-booster.blogspot.ca/2016/02/no-foxtrots-allowed.html} for a description of the issue}, and
is not capable of identifying most of the merges before this date.
\end{itemize}

Of the merges after Sept 4, 2007, in 99.4\% fo them (16,768 out of 16,860)  our heuristic was correct. Overall, we
correctly identified the merge trees of 87.15\% of the merges into master in Linux.

The verification detected no incorrect merges since 2013, two incorrect merges in
2012, and two in 2011; however, the heuristic breaks in October, 15, 2009

>>>>

We used this information to evaluate the accuracy of the merge-tree model extracted from the DAG. The method we followed
started with the extraction of the commit history up to July 20, 2016. We computed the merge tree of every commit until
then. Since Linus Torvalds mostly does merging directly into master, we assumed that every merge by him is the root of a
merge-tree. As described above, the log of a commit usually contains the number of commits in the merge the first 20
summaries of commits being merged. We extracted merges by Linus Torvalds using the command \mycode{log --merges --author='Torvalds} and compared
the number of commits in according to the log with the number of commits in the  merge-tree rooted in this commit. We
also used the summaries of the commits found in the merge (not necessarily all---see above) to make sure those 
commits were in their corresponding merge tree. For example, for the merge in Figure~\ref{sampleMerge} we would expect
that the merge tree rooted at \mycode{8cbd84f} contains 24 commits, and the one-line summaries corresponds to commits in
that merge-tree. We also inspected those with differences to make sure they were true errors.
The results can be summarized as follows:

\begin{itemize}
\item Five merges were false-errors because their logs did not contain accurate information (were probably edited by
  hand). For example in \mycode{42a579a0f...} one commit summary was missing (the line was empty), in \mycode
  {c55d267} the summaries were reordered.
\item The heuristic correctly identified that 79 of Linus merges (between Jun 7, 2014 and Jun 2, 2014) were made to a
  branch (not master). This branch was merged at (\mycode{3f17ea6d..} which contained 6809 commits.
\item The heuristic worked perfectly until Sept 4, 2007, the earliest date that it could be verified.
  Before this date, and until Dec 12, 2006, merges did not include a summary of the commits they included, hence making it
  impossible to verify; during this period, however, we correctly identified the merges by Linus into master. 
\item Before Dec. 12, 2006 (1542 merges) our heuristic breaks due to the
presence of a \textit{foxtrot} commit (\mycode{c436688...}), which confounded the true master branch of a
repository (see \url{http://bit-booster.blogspot.ca/2016/02/no-foxtrots-allowed.html} for a description of the issue).
\end{itemize}

In summary, of the merges after Sept 4, 2007, in 100\% of them (16,860) our heuristic was correct. It failed in 1,542
commits before Dec. 12, 2006 and in 836 it appears to be correct (Dec 7, 2006 to Sept 4, 2007).
